\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\input{config/minimal-resume-config}

\begin{document}
\addtolength{\topmargin}{-0.9in}  

\begin{center}
    % Personal
    % -----------------------------------------------------
    {\fontsize{\sizeone}{\sizeone}\fontspec[Path = fonts/,LetterSpace=15]{Montserrat-Regular} GIORGI KUTATELADZE}
    \\
    \vspace{2mm}
    {\fontsize{1em}{1em}\fontspec[Path = fonts/]{Montserrat-Light} g.kutateli@gmail.com -- Georgia -- \href{http://giorgi.kutateladze.portfolio.s3-website-us-east-1.amazonaws.com/}{My Portfolio}}
\end{center}
% Chapter: Skills
% ------------------------

\chap{SKILLS}{
    \begin{newitemize}
        \item \small Skills: Javascript, Typescript, Angular, Next.js,React,React-Native, Express, Nest.js, Ngrx, Redux, MySQL,mongoDB,firebase, GIt/GItHub,Css/Html/SASS,TailWindcss, Experience with: Python, Php
    \end{newitemize}
}

% Chapter: SUMMARY
% ------------------------

\chap{SUMMARY}{
    
    \project
    {About me and portfolio}
    {}
    {\href{http://giorgi.kutateladze.portfolio.s3-website-us-east-1.amazonaws.com/}{My Portfolio}}
    {\small I fearlessly embrace new languages and tools thanks to my solid grasp of the fundamentals. Beyond the experiences mentioned down below, I\textquotesingle{}ve completed numerous projects showcased on my portfolio website. Additionally, I\textquotesingle{}ve collaborated with fellow developers and contributed to various projects, some of which are on my: \href{https://github.com/vindexTOS}{GitHub} \\}
}

% Chapter: Work Experience
% ------------------------
\chap{EXPERIENCE}{

    \job
    {\small TechFleet}
    {2023 – to this day}
    {\small Junior Developer For Ruminant Project}
    {}
    {
        \begin{newitemize}
          \item \footnotesize The Ruminate Project connects product producers with evaluators in the farming community, enhancing organic produce assessment.
          \item \footnotesize Implemented authentication with email and GoogleAuth, and designed a schema for evaluators.
          \item \footnotesize Conducted frequent meetings with clients, product, and design teams, enhancing soft skills through sprint planning and project feasibility assessments..
         \end{newitemize}
      }
    \job
    {\small Ieworx start-up}
    {\href{https://ieworx-upgrade-emky.vercel.app/}{ieworx.app}}

    {2023 – 2023}
    {\small Full-stack Developer}
    {\begin{newitemize}
        \item \footnotesize Developing a SaaS application to help construction entrepreneurs with tax and legal invoices.
        \item \footnotesize Created a Next.js-based navigation bar and contact form for the start-up's website.
        \item \footnotesize Initially responsible for an Express.js backend for the main project, but production halted until February 2024.
        \item \footnotesize Collaborated for a month and a half with the product owner, gaining valuable team experience.
    \end{newitemize}}
    
    \job
    {\small Chingu}
    {\href{https://github.com/chingu-voyages/v45-tier3-team-34}{Dev-connect}}

    {\small Full-Stack Developer}
    {\begin{newitemize}
        \item \footnotesize I was a participant in Chingu's Voyage 46, where we started working on Upwork clone,Developed a Rest API using Express.js and TypeScript, integrating live chat and notifications via Socket.io, linking it to the React front end.
        \item \footnotesize Implemented JWT-token-based authentication on React, utilizing cookie storage for efficient data persistence and employing the Context API for seamless user data sharing,Created a sophisticated MongoDB schema with distinct roles for companies and developers, featuring functionalities like CV reception and a review system.
        \item \footnotesize Assumed a leadership role, hosted the front end on Netlify and back end on Render.com, adeptly managing merge issues on GitHub, and acquired professional Git proficiency.
    \end{newitemize}}

    
   
    
    
  
    \job
    {\small Optio.ai}
    {\href{https://github.com/vindexTOS/banner_manager_angular}{Banner Manager}}

    {\small Angular}
  
    {  
        \begin{newitemize}
      

 
        \item \footnotesize This project was my first experience with Angular, challange was made by company Optio , Leveraged OOP expertise from Nest.js and PHP, swiftly grasped Angular fundamentals in a day, aided by prior knowledge of Redux, facilitating Ngrx state management.
       \item \footnotesize Received Swagger documentation for a banner management system, implemented nine CRUD endpoints using NGrx effects, and enhanced UI with Angular Material styling. Addressed additional requirements: maintained filter state post-reload, implemented Ngrx for state management, created a comprehensive README with a detailed project video, and included basic unit tests for quality assurance.


    \end{newitemize}}

    }\
 

   
     
\end{document}